Detailed Chemical Abundances with \tc

### 2015-08-28 article/ms.tex
Some text cleanup and boldmath all the things [ci skip]

% Convenient colloquiualisms.
\newcommand\tc{\textit{The Cannon}}

% Convenient maths.
\newcommand\lv{\mathbf{l_n}}
\newcommand\cv{{\mathbf \theta}_\lambda}
\newcommand\given{|}

@@

This form is flexible: the label vector $\lv$ may be linear in just a few labels
or a complex combination of all $K$ available labels. The underlying principle
is that the flux for any pixel from any star is predictable with a very simple
model (generally a polynomial), given the labels. Indeed, \citet{Ness2015}
employ a quadratic-in-labels (see their Equation 8) spectral model using stellar
parameters (effective temperature $T_{\rm eff}$, surface gravity $\log{g}$, and 
metallicity [M/H]) and demonstrate by cross-validation that these labels can be 
measured with a precision of 95~K in $T_{\rm eff}$, 0.24 in $\log{g}$, 0.08 in 
[M/H], with negligible biases.

Utilising a simple polynomial model to predict spectral fluxes is in stark
contrast to parallel efforts in radiative transfer of realistic (3D) stellar 
photospheres. Calculations of this nature are extremely expensive. Indeed, even
with simplications of these models (e.g., interpolated 1D photospheres),
calculating integrated flux requires knowledge of species opacities, detailed 
atomic and molecular information for all contributing elements, solving for
the equation of state, and performing radiative transfer calculations. Given the
simplicity of \tc{} and a quadratic-in-labels spectral model, it is remarkable
that these complex calculations can be simplified so much, whilst maintaining
the typical fidelity reported for high-resolution spectroscopic studies.

@@

\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Baird}{1981}]{b1} Baird S.R., 1981,
%ApJ, 245, 208
\bibitem[Astropy Collaboration et al.(2013)]{astropy} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, AA33
\end{thebibliography}

>>>>

\usepackage{amsmath,amsbsy}

% Convenient colloquiualisms.
\newcommand\article{\textit Article}
\newcommand\tc{\textit{The Cannon}}

% Convenient maths.
\newcommand\K{$\mathbf{K}$}
\newcommand\lv{\bf{\boldsymbol\ell_n}}
\newcommand\cv{{\boldsymbol\theta}_\lambda}
\newcommand\given{|}

@@

This form is flexible: the label vector $\lv$ may be linear in just a few labels
or a complex combination of all $K$ available labels. The underlying principle
is that the flux for any pixel from any star is predictable with a very simple
model (generally a polynomial), given the labels. Indeed, \citet{Ness2015}
employ a quadratic-in-labels (see their Equation 8) spectral model using stellar
parameters (effective temperature $T_{\rm eff}$, surface gravity $\log{g}$, and 
metallicity [M/H]\footnote{\citet{Ness2015} use [Fe/H] in $\lv$, but for the 
sake of distinguishing between overall metallicity and individual abundances,
we opt for [M/H] to describe overall metallicity throughout this \article{}})
and demonstrate by cross-validation that these labels can be 
measured with a precision of 95~K in $T_{\rm eff}$, 0.24 in $\log{g}$, 0.08 in 
[M/H], with negligible biases. It is important to note that these uncertainties
are comparable to those reported by \textit{curve-of-growth} techniques, which
rely on a model atmosphere and the changing strength of atomic absorption lines.

Utilising a simple polynomial model to predict spectral fluxes is a distinctive
method from parallel efforts in radiative transfer of realistic (3D) stellar 
photospheres. Calculations of this nature are extremely expensive. Indeed, even
with simplications of these models (e.g., interpolated 1D photospheres),
calculating integrated flux requires knowledge of species opacities, detailed 
atomic and molecular information for all contributing elements, solving for
the equation of state, and performing radiative transfer calculations. Given the
simplicity of \tc{} and a quadratic-in-labels spectral model, it is remarkable
that these complex calculations can be simplified so much, whilst maintaining
the typical fidelity reported for high-resolution spectroscopic studies.

@@

\begin{thebibliography}{99}
\bibitem[Astropy Collaboration et al.(2013)]{astropy} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, AA33

\bibitem[Ness et al.(2015)]{Ness2015} Ness, M., Hogg, D.~W., 
Rix, H.-W., Ho, A.~Y.~Q., \& Zasowski, G.\ 2015, \apj, 808, 16 
\end{thebibliography}
